Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-02 01-intro.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Introduction \label{intro}}
Denial of service (DoS) and distributed denial of service attacks (DDoS) appeared not very long time after Internet got traction and since then a constant arms race is going on between information providers and attackers who want to knock a certain source of information down. Running a DDoS attack has become a very successful business model due to its general scalable nature, cheapness and lack of protection of information providers by government and law. Most popular and economically effective DDoS attacks are organized with botnets. A botnet agents get installed by many various ways on computers of ordinary people that leads to a very wide geographical distribution of the source of attack that makes blacklisting impossible (in contrast to single source DoS attacks).

@@

>>>>

\section{Introduction}
\label{sec:intro}

% Introduction / Motivation
% Brief introduction about attacks in NDN
% Contributions of the paper

Denial of service (DoS) and distributed denial of service attacks (DDoS) appeared not very long time after Internet got traction and since then a constant arms race is going on between information providers and attackers who want to knock a certain source of information down. Running a DDoS attack has become a very successful business model due to its general scalable nature, cheapness and lack of protection of information providers by government and law. Most popular and economically effective DDoS attacks are organized with botnets. A botnet agents get installed by many various ways on computers of ordinary people that leads to a very wide geographical distribution of the source of attack that makes blacklisting impossible (in contrast to single source DoS attacks).

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2012-12-02 05-evaluation.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algpseudocode}

\graphicspath{{figures/}}

\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
\framebox{\begin{minipage}[c]{0.40 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
\framebox{\begin{minipage}[c]{0.42 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\begin{document}
\maketitle

\begin{abstract}

Distributed Denial of Service attack is an ongoing problem in today's Internet. 
A newly proposed future Internet architecture, Named Data Networking (NDN), lets end users request desired data by sending Interest packets, and the network forwards data packets to end users upon request only. 
Thus, NDN can effectively defeat the existing DDoS attacks, however it can be subject to new types of DoS attacks, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding attacks. 
We use simulations to evaluate the design and our results show that our proposed solution can respond to Interest flooding attacks quickly, and that the inherent flow-balance property of NDN (i.e., one Interest packet retrieves at most one Data packet) can be used as a basis for effective DDoS mitigation algorithms.

\end{abstract}

\begin{IEEEkeywords}
Information-Centric Networks, Named-data Networking, Denial-of-Service
\end{IEEEkeywords}

\input{intro}
\input{ndn-overview}
\input{ddos-ndn}

\section {Interest Flooding in NDN}

\section {Countermeasures against Interest flooding}

Basic limits, probablity based on statistics, and dynamic window adjustment

(Description of each of the above, and their implications)

\input{design}

\section{Evaluation}
\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

@@

\subsection{Results from probability based on statistics}

\subsection{Results from dynamic window adjustment}

\section{Implications/Analysis}
Lessons we learnt, comparison of different mitigation techniques. 
Adapting these to mitigate other DDoS attacks.

\section{Conclusions and Future Work}

\bibliographystyle{plain}
\bibliography{references}

\appendix

\input{algos/physical-limits.tex}

\input{algos/fair-queueing.tex}

\input{algos/dynamic-limits.tex}

\input{algos/probabilistic.tex}

\input{algos/stats.tex}

\end{document}

>>>>

\section{Evaluation of Interest flooding mitigation methods}
\label{sec:evaluation}

\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

@@

### 2012-12-02 paper.tex
Adding a couple of figures, more to come
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@843 df1a90cd-247b-4364-bdaf-287a704eb499
Adding figures (topology sketch and simulation results) for large scale
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@845 df1a90cd-247b-4364-bdaf-287a704eb499
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

@@

\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
\framebox{\begin{minipage}[c]{0.40 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
\framebox{\begin{minipage}[c]{0.42 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

@@

\input{intro.tex}
\input{ndn-overview.tex}
\input{ddos-ndn.tex}
\section { Interest Flooding in CCN }

\section {Countermeasures against Interest flooding}

Basic limits, probablity based on statistics, and dynamic window adjustment

(Description of each of the above, and their implications)

\section {Evaluation}
\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}

We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways. First, we need to understand how each method works on a very ground level of a just few nodes and links. Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes. To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy. As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.

\input{simulation-emulation.tex}

\subsection{Results from probability based on statistics}

\subsection{Results from dynamic window adjustment}

\input{large-scale.tex}

\section{Implications/Analysis}
Lessons we learnt, comparison of different mitigation techniques. 
Adapting these to mitigate other DDoS attacks.

\section{Conclusions and Future Work}

@@

\appendix

\input{algos/physical-limits.tex}

\input{algos/fair-queueing.tex}

\input{algos/dynamic-limits.tex}

\input{algos/probabilistic.tex}

\input{algos/stats.tex}

>>>>

\title{Mitigating Interest Flooding DDoS Attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

@@

\graphicspath{{figures/}}

@@

\input{01-intro}

\input{02-ndn-background}

\input{03-interest-flooding}

\input{04-design}

\input{05-evaluation}

\input{06-related}

\input{07-discussion}

\input{08-conclusion}

@@
